### 2011-02-12 Text/paper.tex
Added part of the results. Need to perform bunch of simulations with smaller capillary numbers and better grid.

\section{Variation bubble length}
The works of \citet{heil-threedim} of \citet{wang-non-circular} show the variation of the bubble
thickness through the length of
bubble. The length variation is presented in Fig. \ref{fig:thickness:variation:ca:ten} and
Fig.\ref{fig:wang:bubble:shape}. One can see that it takes a certain distance for the diagonal
radius to be equal to the axial even in the symmetric regime.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/variationoverlength.eps}
\caption{The variation of the bubble length for capillary number $Ca=10$. The x-axis scaled to
half-width of the microchannel height.  \label{fig:thickness:variation:ca:ten}}
\end{figure}
We want to obtain the same characteristics as indicated in Fig.
\ref{fig:thickness:variation:ca:ten}. One can see that the difference between diagonal radius and
usual radius is of order of $4\%$. That means it's 2 percent of the channel height. If the
simulation is conducted by the grid $50\mathrm{x}50$ in the cross section that means that we will
see the difference in one grid node. Therefore the grid is $52\mathrm{x}52\mathrm{750}$. Here we
conduct a scaling:
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma}
\end{equation}
The parameters for the binary liquid problem are chosen as $A=0.04$ and $k=0.01$. Therefore the
surface tension is:
\begin{equation}
\sigma = \sqrt{\frac{8 k A}{9}}=0.0596
\end{equation}
The relaxation times for liquid and gas are taken as, $\tau_{gas}=0.7$ and $\tau_{liq}=2.5$,
therefore the viscosities ratio is $10$.
\begin{equation}
\begin{aligned}
&10=\frac{\frac{2}{3} U_{bubble}}{0.0596},
&U_{bubble}=0.894
\end{aligned}
\end{equation}
which is quite high for the lattice Boltzmann method. We can decrease the ratio by scaling
parameters $k$ and $A$ while keeping the interface thickness. Let us choose parameters as $k=0.001$
and $A=0.004$, therefore the mobility should be adjusted to address the issue with small parameters
and small surface tension in this case. It parameters are chosen as $A=0.004$ and $k=0.001$ then
the velocity of the bubble is  $0.0894$. Therefore we can adjust the pressure gradient to plug it
into the bubble initialization:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=\frac{8}{N_y^2} \gamma Ca=0.0001907,
\end{equation}
which is quite high for lattice Boltzmann simulations. Therefore probably one more time the surface
tension needs to be reduced. {\color{red} Many authors state that increasing mobility kills the
proper results of simulations}. 
The film thickness as it is seen from the picture is taken as $70$ percent of the half channel.
Therefore the initalization width is $0.15*50=7.5$.

>>>>

\section{Variation bubble length}
The works of \citet{heil-threedim} of \citet{wang-non-circular} show the variation of the bubble
thickness through the length of
bubble. The length variation is presented in Fig.\ref{fig:thickness:variation:ca:ten} and
Fig.\ref{fig:wang:bubble:shape}. While Fig. \ref{fig:wang:bubble:shape} indicates that the diagonal
radius has a variation for the rather small capillary numbers as $Ca<0.1$, another profile is
presented for the $Ca=10$ and shows the variation for the diagonal radius. We examined a bunch of
different capillaries numbers to present the diagonal radius variations over the length:
The axis and diagonal radiuses variation over the bubble are shown in Figure
\ref{fig:bubble:variation:capillaries}. The rather small capillary numbers one can see the increase
in the rear menisci of the diagonal radius which coincides with the results of
\citet{wang-non-circular}.
\begin{figure}[ht]
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_36.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_61.eps}\\
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_88.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/bubble_length_ca_117.eps}\\
\caption{The radiuses variations for the capillary number $Ca=0.46$.
One can see the diagonal radius different from the axial radius near the front of the tip which is
somehow coincides with the results of
\citet{heil-threedim}. The results are presented for the
capillary numbers (from left to right, top to bottom)
$0.36$, $0.61$, $0.88$, $1.17$. \label{fig:bubble:variation:capillaries}}
\end{figure}
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/variationoverlength.eps}
\caption{The variation of the bubble length for capillary number $Ca=10$. The x-axis scaled to
half-width of the microchannel height.  \label{fig:thickness:variation:ca:ten}}
\end{figure}

Concerning results indicated in Fig.
\ref{fig:thickness:variation:ca:ten} simulations are unstable that means one needs to work with
small surface tension ({\color{red} See results of Pagonabarraga}). One can see that the difference
between diagonal radius and
usual radius is of order of $4\%$. That means it's 2 percent of the channel height. If the
simulation is conducted by the grid $50\mathrm{x}50$ in the cross section that means that we will
see the difference in one grid node. Therefore the grid is $52\mathrm{x}52\mathrm{750}$. Here we
conduct a scaling:
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma}
\end{equation}
The parameters for the binary liquid problem are chosen as $A=0.04$ and $k=0.01$. Therefore the
surface tension is:
\begin{equation}
\sigma = \sqrt{\frac{8 k A}{9}}=0.0596
\end{equation}
The relaxation times for liquid and gas are taken as, $\tau_{gas}=0.7$ and $\tau_{liq}=2.5$,
therefore the viscosities ratio is $10$.
\begin{equation}
\begin{aligned}
&10=\frac{\frac{2}{3} U_{bubble}}{0.0596},
&U_{bubble}=0.894
\end{aligned}
\end{equation}
which is quite high for the lattice Boltzmann method. We can decrease the ratio by scaling
parameters $k$ and $A$ while keeping the interface thickness. Let us choose parameters as $k=0.001$
and $A=0.004$, therefore the mobility should be adjusted to address the issue with small parameters
and small surface tension in this case. It parameters are chosen as $A=0.004$ and $k=0.001$ then
the velocity of the bubble is  $0.0894$. Therefore we can adjust the pressure gradient to plug it
into the bubble initialization:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=\frac{8}{N_y^2} \gamma Ca=0.0001907,
\end{equation}
which is quite high for lattice Boltzmann simulations. Therefore probably one more time the surface
tension needs to be reduced. {\color{red} Many authors state that increasing mobility kills the
proper results of simulations}. 
The film thickness as it is seen from the picture is taken as $70$ percent of the half channel.
Therefore the initalization width is $0.15*50=7.5$.
